---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Diseños experimentales: Aleatorización

  * Diseño de grupo de control pretest-postest
  * Cuatro grupo de Salomon
  * Diseño de grupo de control postest

## De manera Intuitiva
## Algo de historia
## De manera formal
## Replicando un caso de estudio externo: Atención a Crisis, Nicaragua

  + Tiempo 0: April–May 2005
  + Tiempo 1: July–August 2006
  + Tiempo 2: August 2008 and May 2009
  
Población: The Atención a Crisis pilot program was implemented between November 2005 and December 2006 by the Ministry of the Family in six municipalities in rural Nicaragua.

Asignación: 56 intervention and 50 control communities were randomly selected through a lottery.

```{r}
rm(list = ls())
library(haven)
library(dplyr)
library(texreg)
bd<-read_dta("/Users/alvarolimber/Dropbox/iEvaluation_R/!library/cedlaBasico/Parte-Practica/Asignacion-Aleatoria/Macours-et-al.dta")

bd<-bd %>% filter(is.na(unique_05)==F)
bd %>% group_by(unique_05,T) %>% summarise(tx=n())
```

This process resulted in the identification
of 3,002 households to participate in the program

  + Basic
  + Basic + training 
  + Basic + grant
  
Households in Group 1 were offered a cash transfer, paid to the “titular” every
two months. For households with children ages 0–5, this transfer was in principle
conditional on regular preventive health check-ups. However, in practice, this conditionality
was not monitored, and households were not penalized for noncompliance.
Households with children between 7 and 15 years old who had not finished primary
school received an additional educational transfer, conditional on the school enrollment
and regular attendance of those children. The education conditionality was
monitored in practice. The basic Atención a Crisis intervention was modeled after
an earlier CCT program in Nicaragua, the Red de Protección Social (RPS).5 On
average, transfers made to this group represented 15 percent of per capita expenditures
of the average recipient household in our sample over the year in which it was
implemented.6 We refer to this treatment as the basic treatment.
Households in Group 2 received a cash transfer that was identical to that received
by households in Group 1. In addition, they were offered a scholarship that allowed
one of the household members to choose among a number of vocational training
courses offered at the municipal headquarters. These household members also participated
in labor market and business-skill training workshops organized in their
own communities. We refer to this treatment as the training package.
Households in Group 3 received a cash transfer that was identical to that received
by households in Group 1. In addition, they were offered a lump-sum payment to
start a small nonagricultural activity. This lump sum was conditional on the household
developing a business development plan. It was paid out between the end of
May and September 2006.7 The value of the lump-sum payment represented approximately
11 percent of per capita expenditures of the average recipient household
over the year in which it was implemented. A household in Group 3 therefore was
eligible for transfers equivalent to approximately 26 percent of annual expenditures.
We refer to this treatment as the lump-sum payment package.  

```{r}
library(miceadds)#lm.cluster
library(sandwich)
library(texreg)#extract
bd %>% select(z_language_06,T)
options(scipen=999)

m0<-lm(z_language_06~T,data = bd)
m1<-lm.cluster(z_language_06~T,data = bd,cluster = "unique_05")
m2<-lm.cluster(z_language_08~T,data = bd,cluster = "unique_05")

summary(m0)
summary(m1)
summary(m2)
extract(m0)
bdh<-bd %>% group_by(hogarid_old) %>% mutate(pp=1,pp=cumsum(pp)) %>% filter(pp==1)

m4<-lm.cluster(scale(cons_tot_pc_08)~TREAT1+TREAT2+TREAT3,data = bdh,cluster = "unique_05")
summary(m4)
```

## Estudio de caso Bolivia: Programa X

## Validez del diseño
## Muestra y poder

$$H_0: \mu_T-\mu_C=0$$
$$H_1: \mu_T-\mu_C\neq 0; \quad \mu_T-\mu_C= d$$

  * Error de tipo I: $\alpha$, falso positivo, Rechazar algo verdadero (rechazar impacto dado que existe)
  * Error de tipo II: $\beta$, falso negativo, Aceptar algo falso (declarar impacto cuando no existe)
  
| Realidad | ~R HO    | R H0    |
|----------|----------|---------|
| H0 V     | $1-\alpha$ | $\alpha$  |
| H0 F     | $\beta$    | $1-\beta$ |  

Tamaño del efecto (effect size) y el efecto mínimo detectable.

$$\delta=\frac{\mu_T-\mu_C}{\sigma}$$

$$n=\frac{\left(Z_{1-\alpha/2}+Z_\beta\right)^2}{\delta^2}$$
```{r}
library(CRTSize)#cluster
library(pwr)#simple
n4means(0.30,1,10,0.05)
pwr.t.test(d=1/2,sig.level = 0.05,power = 0.9)
```

## En R



## Creando funciones
## Empleando la librería 